The Effect of Education Adjustment on Parameter Estimates

### 2014-11-04 Articles/Article_JAE_2014/Education Investigation.Rmd
Added energy calcs.

```{r HistoricalData, warning=FALSE, fig.cap="Historical GDP, capital stock, and thermal energy data."}
mdata <- melt(historicalData, 
              measure.vars = c("iGDP", "iK", "iQp"), 
              variable.name = "variable",
              value.name = "value")
mapping <- aes(x=Year, y=value, group=variable, linetype=variable)
ggplot(mdata, mapping=mapping) + 
  geom_line(mapping) +
  xy_theme() +
  xlab("") + 
  ylab("Indexed (1973=1)")
```

@@

Finally, fit using education-adjusted formal and informal labor data ($iLfie$)
```{r FormalPlusInformalPlueEducation}
naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iYear, 
                    data = historicalData, constrained = TRUE))
```

@@

>>>>

```{r HistoricalData, warning=FALSE, fig.cap="Historical GDP, capital stock, and thermal energy data."}
mdata <- melt(historicalData, 
              measure.vars = c("iGDP", "iK", "iQp", "iQf"), 
              variable.name = "variable",
              value.name = "value")
mapping <- aes(x=Year, y=value, group=variable, linetype=variable)
ggplot(mdata, mapping=mapping) + 
  geom_line(mapping) +
  xy_theme() +
  xlab("") + 
  ylab("Indexed (1973=1)")
```

@@

Finally, fit using education-adjusted formal and informal labor data ($iLfie$)
```{r FormalPlusInformalPlusEducation}
naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iYear, 
                    data = historicalData, constrained = TRUE))
```

@@

Effect of Energy
----------------------------------------------------------------

Now, we use the Cobb-Douglas equation with an energy term.

\begin{equation}
  GDP = \mathrm{e}^{\lambda t} k^\alpha l^\beta e^\gamma
\end{equation}

under the constraint $\alpha + \beta + \gamma = 1$ to ensure constant returns to scale.

First, we fit using education-adjusted formal and informal labor data ($iLfie$)
and primary thermal energy ($iQp$).
```{r FormalPlusInformalPlusEducationWithPrimaryEnergy}
res <- naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iQp + iYear, 
                           data = historicalData, constrained = TRUE))
row.names(res)<-NULL
res
```

Next, we fit using education-adjusted formal and informal labor data ($iLfie$)
and final thermal energy ($iQf$).
```{r FormalPlusInformalPlusEducationWithFinalEnergy}
res <- naturalCoef(cdModel(formula = iGDP ~ iK + iLfie + iQf + iYear, 
                           data = historicalData, constrained = TRUE))
row.names(res)<-NULL
res
```
